---
title: "Untitled"
author: "vincy hu"
date: "5/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(dplyr)
library(lmPerm)
```


# t-test 
1. overview of t-test  
  + a good approximation to the permutation (shuffled) distribution was the t-test! Since there were not enough computing power for permutation test at that time    
  + used for the very common two-sample comparison — A/B test — in which the data is numeric.  
  + t-test is testing for difference of sample mean

2. Questions to mark  
  + what's the prerequisite to run the t-test
  +
```{r}
t.test(Time ~ Page, data=session_times, alternative='less' )
```

In a resampling mode, we structure the solution to reflect the observed data and
the hypothesis to be tested, not worrying about whether the data is numeric or
binary, sample sizes are balanced or not, sample variances, or a variety of other
factors.


# ANOVA - Analysis of variance
1. Overview
  + It's comparing mean of a numeric value in different group, if it's one-way, then one type of group deconstruction(for example, the different type of diet).
  + If there are only two category in the one-way variable, then it's the same as two-sample t-test
  + You can see that ANOVA, then two-way ANOVA, are the first steps on the road toward a full statistical model, such as regression and logistic regression

2. Test statistics
  + F-statistic is based on the ratio of the variance across group means (i.e., the treatment effect) to the variance due to residual error
```{r}
# one-way anova

png(filename=file.path(PSDS_PATH, 'figures', 'psds_0306.png'),  width = 4, height=4, units='in', res=300)

ggplot(four_sessions, aes(x=Page, y=Time)) + 
  geom_boxplot() +
  labs(y='Time (in seconds)') +
  theme_bw()

dev.off()


summary(aovp(Time ~ Page, data=four_sessions)) # permutation test to compare the variance 
summary(aov(Time ~ Page, data=four_sessions)) # one-way anova
```
  

